Hockey Enforcers

### 2023-06-14 HocketEnforcersReport.Rmd
Report Markdown.

```{r}
library(survival)
#Defining the survival variab=le
dat$age
dat$Surv <- Surv(dat$age,dat$dead)
```

@@

#Kaplan meier plot
Enforcers (blue), as defined by the paper, vs non-enforcers (red)
```{r}
library(ggsurvfit)
survfit2(Surv ~ EF, data = dat) %>% 
  ggsurvfit() +
  labs(
    x = "Year",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval()
```

#Cox model with Total.fights as a covariate.  
```{r}
a <- coxph(Surv ~ Total.Fights + GP.x + Ht + Wt + DOB.Year + Pos , data = dat)
summary(a)
```
#Cox model with EF as a covariate.  
```{r}
a <- coxph(Surv ~ EF + GP.x + Ht + Wt + DOB.Year + Pos , data = dat)
summary(a)
```

#Matching
Now repeat this with matching.  
```{r}
library(MatchIt)
#Mathing on EF
m.out <- matchit(EF ~ GP.x + Ht + Wt + DOB.Year + Pos, data = dat, ratio = 1)
dataMatched <- match.data(m.out)

@@

#Effect of Enforcer on hazard ratio after matching
n = 640 here.  
```{r}
coxph(Surv ~ EF, data = dataMatched)
```

```{r}
coxph(Surv ~ EF + GP.x + Ht + Wt + DOB.Year + Pos, data = dataMatched)
```
#Conditioning on dead people 
All the significance disappears.  
```{r}
dataMatched %>% filter(dead) %>% group_by(EF) %>% summarise(mnage = mean(as.numeric(age)), mnwt = mean(Wt))

@@

b <- lm(age ~ EF + Wt, data = dataMatched[dataMatched$dead,])
summary(b)
```
#Various stuff
```{r}
dataMatched$age <- as.numeric(dataMatched$age)
b <- lm(age ~ Wt, data = dataMatched[dataMatched$dead,])
summary(b)

@@

#Simulating from a coxph model with a Weibull baseline
#Everything below here is still nonsense.  
This is far from complete....
```{r}

>>>>

```{r}
library(survival)
#Defining the survival variable
dat$Surv <- Surv(dat$age,dat$dead)
```

@@

# Kaplan meier plot
Enforcers (blue), as defined by the paper, vs non-enforcers (red)
```{r}
library(ggsurvfit)
survfit2(Surv ~ EF, data = dat) %>% 
  ggsurvfit() +
  labs(
    x = "Year",
    y = "Overall survival probability"
  ) + 
  add_confidence_interval()
```

# Cox model with Total.fights as a covariate.  
```{r}
a <- coxph(Surv ~ Total.Fights + GP.x + Ht + Wt + DOB.Year + Pos , data = dat)
summary(a)
```
# Cox model with EF as a covariate.  
```{r}
a <- coxph(Surv ~ EF + GP.x + Ht + Wt + DOB.Year + Pos , data = dat)
summary(a)
```

# Matching
Now repeat this with matching.  
```{r}
library(MatchIt)
#Mathing on EF
m.out <- matchit(EF ~ GP.x + Ht + Wt + DOB.Year + Pos, data = dat, ratio = 1)
dataMatched <- match.data(m.out)

@@

# Effect of Enforcer on hazard ratio after matching
n = 640 here.  
```{r}
coxph(Surv ~ EF, data = dataMatched)
```

```{r}
coxph(Surv ~ EF + GP.x + Ht + Wt + DOB.Year + Pos, data = dataMatched)
```
# Conditioning on dead people 
All the significance disappears.  
```{r}
dataMatched %>% filter(dead) %>% group_by(EF) %>% summarise(mnage = mean(as.numeric(age)), mnwt = mean(Wt))

@@

b <- lm(age ~ EF + Wt, data = dataMatched[dataMatched$dead,])
summary(b)
```
# Various stuff
```{r}
dataMatched$age <- as.numeric(dataMatched$age)
b <- lm(age ~ Wt, data = dataMatched[dataMatched$dead,])
summary(b)

@@

# Simulating from a coxph model with a Weibull baseline
# Everything below here is still nonsense.  
This is far from complete....
```{r}
